---
title: "R examples"
author: "LB"
date: "2022-12-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ex

For en given matrix $C$

```{r, echo=FALSE}
v1 = c(1,0,0)
v2 = c(0.1,0,1.1)
C = rbind(v1,v2)
print(C)
```

Og en vektor $t$ kvadreret og sat diagonalt i en matrix
```{r, echo=FALSE}
t = c(1,2,3)
print(t)
W = matrix(diag(sqrt(t)), ncol = length(t))
print(W)
```

En operator-matrix $M$ 
```{r, echo=FALSE}
M = diag(1,length(t), length(t))
print(M)
M[row(M)==col(M)+1] = -1
print(M)
print(solve(M))
```
$A$ er en NxN matrix
```{r, echo=FALSE}
A = (C %*% solve(M)) %*% solve(W)
print(A)
```

Den pseudoinverse $X$:
```{r, echo=FALSE}
X = t(A) %*% (solve(A %*% t(A)))
print(X)
```

En ikke nærmere defineret matrix:
```{r, echo=FALSE}
d = matrix(0, dim(X)[1], 1)
d[row(d)==1] = 1
Y = (C %*% solve(M)) %*% d
print(Y)
```

En vektor $P$ og en incrementor og d* og d
```{r, echo=FALSE}
P = c(0.98,0.95)
print(P)

mI = P - Y;
print(mI)

mD = X %*% mI;
print(mD)

df = solve(M) %*% ((solve(W) %*% mD) + d);
print(df)
```




```{r cashflows}

# creating company data frame
comp.data <- data.frame(
 
# bond ids
# data members
comp_id = c (1:3),
 
# company names
comp_name = c("Geeks", "For", "Geeks"),
growth = c(16000, 14000, 12000),
 
# company start dates
# data members
comp_start_date = as.Date(c("02/05/10", "04/04/10", "05/03/10"))
)
print(comp.data)
```

## Including code

You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

## Notes and references
* For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
* Add the `echo = FALSE` parameter to the code chunk to prevent printing of the R code that generated the plot.
    + Item 2a
    + Item 2b
    
## Shortcuts
* Ctrl + Shift + K => Knit
* Ctrl + D => Delete line of code



